\subsection{Assumptions}
This probe makes a number of assumptions.
First, it assumes that the injection rate of the GC or other injector (assuming there is one and it is active) is high enough that testing each TTL value in the binary search for the minimum TTL value required yields a significant chance that an injection will be seen.
Injection rates seen by Marczak et al. were about 1.75\%~\cite{Marczak2015}.
Second, it assumes that one or more of the files for which the crawlers scraped URIs is being targeted by the GC or other injector.
In the case of the GitHub DDoS, only a single file was seen to be targeted.
Finally, it assumes that the IP address from which the probe is run is not being filtered.
Marczak et al. observed that no injections were made in response to requests originating from one of four test IP addresses.
\subsection{Next Steps}
Several technical improvements can be made to the probing process:
\begin{itemize}\addtolength{\itemsep}{-.35\baselineskip}
	\item As the probe for a given domain can often run for a long time, it may be advantageous to perform multiple traceroutes throughout the course of a probe to increase temporal proximity in the distance estimates.
		Additionally, a better estimate for the distance of a domain's servers may be possible, perhaps using the TTL value required to download other files from that domain.
	\item The full-site crawler can be optimized for broad crawls.
		Several suggestions are offered on the Scrapy website: \url{http://doc.scrapy.org/en/latest/topics/broad-crawls.html}
	\item The crawlers can also do a better job at scraping JS URIs.
		At present, all relative URIs and URIs containing single quotes are ignored.
\end{itemize}

An obvious extension to these one-off probes would be a persistent probe running in a slow loop so as to avoid detection and wasting network resources.
By triggering alerts when suspicious files are found, this persistent probe would be in a good position to detect future GC activity.
It may also be worth testing other injection detection tools with the file injector described in \autoref{testing}.